---
title: "Regression Modelling Coursework"
author: "Sean Longman"
date: "14/10/2021"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(tidyverse)
library(olsrr)
library(ResourceSelection)
library(pastecs)
library(openxlsx)
library(lmtest)
```

## Load the demographic and health survey data
```{r}
dem_health_surv_orig <- read_sav("assignment data/demographic and health survey.sav")
dem_health_surv <- dem_health_surv_orig # separate variable to restart in case of error rather than reload data
```

## Separating categorical variables into dummy variables
```{r}
# Turn into character before turning into factor. Numeric to factor sometimes has issues in R due to how R codes factor variables
dem_health_surv[,4:9] <- lapply(dem_health_surv[,4:9], as.character) 

# turn into factor
dem_health_surv[,4:9] <- lapply(dem_health_surv[,4:9], factor) 

# Do a summary to decide which categories to turn into reference categories
summary(dem_health_surv[,4:9])

# Create dummies, turning categories with least number of obs into reference categories
# mutate allows to alter multiple varaibles within data frame in one code block and works with dplyr pipe operator (%>%) meaning
# I don't need to always put dem_health_surv$, can just reference variable without data frame
dem_health_surv <- dem_health_surv %>%
  mutate(
    HW5_ltn2 = case_when(HW5 < -2 ~ 1, TRUE ~ 0), # ltn2 = less than negative 2, case_when is another version of ifelse function from dplyr package
    male = case_when(SEX == 0 ~ 1, TRUE ~ 0),
    bf1 = case_when(BREASTFEED == 1 ~ 1, TRUE ~ 0),
    bf2 = case_when(BREASTFEED == 2 ~ 1, TRUE ~ 0),
    bf3 = case_when(BREASTFEED == 3 ~ 1, TRUE ~ 0),
    bf4 = case_when(BREASTFEED == 4 ~ 1, TRUE ~ 0),
    momedu0 = case_when(MOMEDU == 0 ~ 1, TRUE ~ 0),
    momedu1 = case_when(MOMEDU == 1 ~ 1, TRUE ~ 0),
    momedu2 = case_when(MOMEDU == 2 ~ 1, TRUE ~ 0),
    wealth1 = case_when(WEALTHIND == 1 ~ 1, TRUE ~ 0),
    wealth2 = case_when(WEALTHIND == 2 ~ 1, TRUE ~ 0),
    wealth3 = case_when(WEALTHIND == 3 ~ 1, TRUE ~ 0),
    wealth4 = case_when(WEALTHIND == 4 ~ 1, TRUE ~ 0),
    wealth5 = case_when(WEALTHIND == 5 ~ 1, TRUE ~ 0),
    rural = case_when(RESIDENCE == 2 ~ 1, TRUE ~ 0),
    urban = case_when(RESIDENCE == 1 ~ 1, TRUE ~ 0),
    numchild1 = case_when(LIVCHN == 1 ~ 1, TRUE ~ 0),
    numchild2 = case_when(LIVCHN == 2 ~ 1, TRUE ~ 0),
    numchild3 = case_when(LIVCHN == 3 ~ 1, TRUE ~ 0)
  )
```
## Create scatter plots of continuous variables to look for correlation
```{r}
#png("contin_var_scatterplots.png")
plot(dem_health_surv[,c("HW5", "MOMAGE","MOMWEIGHT")],
     main = "Scatter of height-for-age z-score, mother's age and mother's weight",
)
#dev.off()
stat.desc(dem_health_surv[,1:3])
# typeof(table(dem_health_surv$WEALTHIND, dem_health_surv$RESIDENCE))
```
```{r}
cor(dem_health_surv[,c("HW5", "MOMAGE", "MOMWEIGHT")], method = "pearson", use = "complete.obs")
```

##Boxplot of dependent variable HW5
```{r}
boxplot(dem_health_surv$HW5)
```
## tables looking at correlation between dependent and independent variables
```{r}
table(dem_health_surv$HW5_ltn2, dem_health_surv$SEX, dnn = c("HW5","SEX"))
table(dem_health_surv$HW5_ltn2, dem_health_surv$BREASTFEED, dnn = c("HW5","BREASTFEED"))
table(dem_health_surv$HW5_ltn2, dem_health_surv$MOMEDU, dnn = c("HW5","MOMEDU"))
table(dem_health_surv$HW5_ltn2, dem_health_surv$WEALTHIND, dnn = c("HW5","WEALTHIND"))
table(dem_health_surv$HW5_ltn2, dem_health_surv$RESIDENCE, dnn = c("HW5","RESIDENCE"))
table(dem_health_surv$HW5_ltn2, dem_health_surv$LIVCHN, dnn = c("HW5","LIVCHN")) #29.8
```
## Linear models
```{r}
mlr_full_model <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$male + dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3 + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$rural + dem_health_surv$numchild2 + dem_health_surv$numchild3)

summary(mlr_full_model)
```
```{r}
## rural, male and breastfeed are all insignificant. Comparing p-values on male and rural, rural has a higher p-value so will compare rural vs. bf.
## Creating the models, looking at the adjusted R squared values with each variable removed, the model with the breast feed variable has a higher R squared value than the model
## with rural in it and an anova test shows it is statistically significantly different so remove the rural variable
test_fit1 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$male + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3 + dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3)

test_fit2 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$male + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$rural + dem_health_surv$numchild2 + dem_health_surv$numchild3)

summary(test_fit1)
summary(test_fit2)
anova(test_fit1, test_fit2)
```
```{r}
mlr_bw_elim_v1 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$male + dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3 + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3)

summary(mlr_bw_elim_v1)
```

```{r}
## bf and male are insignificant.Looking at the Adjusted R-squared with each variable removed, model with bf variable has a higher R-Squared and using an anova test, the R squared value is statistically significantly different
## Therefore remove male variable
test_fit3 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3 + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3)

test_fit4 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$male + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3)

summary(test_fit3)
summary(test_fit4)

anova(test_fit3, test_fit4)

```
```{r}
mlr_bw_elim_v2 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3 + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3)
summary(mlr_bw_elim_v2)
```
### final backward elimination model
```{r}
## Removing bf as insignificant
mlr_bw_elim_final <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3)
summary(mlr_bw_elim_final)
```
###residual analysis
```{r}
mlr_bw_elim_final_res <- resid(mlr_bw_elim_final)
{plot(fitted(mlr_bw_elim_final), mlr_bw_elim_final_res)
abline(0,0)}
```
```{r}
{hist(scale(mlr_bw_elim_final_res), freq = FALSE, breaks=40)
curve(dnorm,add=TRUE)}
```
##Stepwise model selection
```{r}
## Repeat model selection with stepwise
## Models with one of the variables
summary(lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE))
summary(lm(dem_health_surv$HW5 ~ dem_health_surv$MOMWEIGHT))
summary(lm(dem_health_surv$HW5 ~ dem_health_surv$male))
summary(lm(dem_health_surv$HW5 ~ dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3))
summary(lm(dem_health_surv$HW5 ~ dem_health_surv$momedu0 + dem_health_surv$momedu1))
summary(lm(dem_health_surv$HW5 ~ dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4))
summary(lm(dem_health_surv$HW5 ~ dem_health_surv$rural))
summary(lm(dem_health_surv$HW5 ~ dem_health_surv$numchild2 +dem_health_surv$numchild3 ))

```

```{r}
stepwise_model_v1 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMWEIGHT)
summary(stepwise_model_v1)

stepwise_model_v2 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMWEIGHT + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4)
summary(stepwise_model_v2)

stepwise_model_v3 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMWEIGHT + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$momedu0 + dem_health_surv$momedu1)
summary(stepwise_model_v3)

stepwise_model_v4 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMWEIGHT + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$rural)
summary(stepwise_model_v4)
#Remove rural var as not significant to the 95% level
stepwise_model_v5 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMWEIGHT + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3)
summary(stepwise_model_v5)

#Remove bf var as not significant to the 95% level
stepwise_model_final <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMWEIGHT + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$momedu0 + dem_health_surv$momedu1)
summary(stepwise_model_final)
```
##Compare models
```{r}
anova(stepwise_model_final,mlr_bw_elim_final)
```
##Interaction variable intro
```{r}
mlr_full_model_inter <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$male + dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3 + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$rural + dem_health_surv$numchild2 + dem_health_surv$numchild3 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild2 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild3)

summary(mlr_full_model_inter)
```

```{r}
## rural, male and breastfeed are all insignificant. Comparing p-values on male and rural, rural has a higher p-value so will compare rural vs. bf.
## Creating the models, looking at the adjusted R squared values with each variable removed, the model with the breast feed variable has a higher R squared value than the model
## with rural in it and an anova test shows it is statistically significantly different so remove the rural variable
test_fit1 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$male + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3 + dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild2 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild3)

test_fit2 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$male + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$rural + dem_health_surv$numchild2 + dem_health_surv$numchild3 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild2 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild3)

summary(test_fit1)
summary(test_fit2)
anova(test_fit1, test_fit2)
```

```{r}
bw_mlr_inter_v1 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$male + dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3 + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild2 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild3)

summary(bw_mlr_inter_v1)
```
```{r}
## bf and male are insignificant.Looking at the Adjusted R-squared with each variable removed, model with bf variable has a higher R-Squared and using an anova test, the R squared value is statistically significantly different
## Therefore remove male variable
test_fit3 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3 + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild2 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild3)

test_fit4 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$male + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild2 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild3)

summary(test_fit3)
summary(test_fit4)

anova(test_fit3, test_fit4)
```
```{r}
bw_mlr_inter_v2 <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$bf1 + dem_health_surv$bf2 + dem_health_surv$bf3 + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild2 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild3)

summary(bw_mlr_inter_v2)
```
```{r}
bw_mlr_inter_final <- lm(dem_health_surv$HW5 ~ dem_health_surv$MOMAGE + dem_health_surv$MOMWEIGHT + dem_health_surv$momedu0 + dem_health_surv$momedu1 + dem_health_surv$wealth1 + dem_health_surv$wealth2 + dem_health_surv$wealth3 + dem_health_surv$wealth4 + dem_health_surv$numchild2 + dem_health_surv$numchild3 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild2 + dem_health_surv$MOMWEIGHT*dem_health_surv$numchild3)

summary(bw_mlr_inter_final)
```
```{r}
bw_mlr_inter_final_res <- resid(bw_mlr_inter_final)
{plot(fitted(bw_mlr_inter_final), bw_mlr_inter_final_res)
abline(0,0)}
```

```{r}
{hist(scale(bw_mlr_inter_final_res), freq = FALSE, breaks=40)
curve(dnorm,add=TRUE)}
```
```{r}
anova(bw_mlr_inter_final,mlr_bw_elim_final)
```
## Exploratory data analysis for logit model
```{r}
table(dem_health_surv$HW5_ltn2)
1133/(2666 + 1133)
```

```{r}
colors <- c("#FDAE61","#66BD63","#FF0000")#,"#0000FF","#FF00FF")
plot(dem_health_surv$MOMWEIGHT, dem_health_surv$HW5_ltn2, col = colors[factor(dem_health_surv$LIVCHN)],
     xlab = "MOMWEIGHT", ylab = "malnourished")
legend("center", legend = c("Less than 3 living children","3-4 living children","5+ living children"), pch = 19, col = colors)
```
```{r}
cols <- rainbow(2, s = 0.5)
boxplot(dem_health_surv$MOMWEIGHT ~ dem_health_surv$HW5_ltn2 + dem_health_surv$LIVCHN,
        xlab = "momedu", ylab = "weight", names = c("1","1","2","2","3","3"), col = cols)
par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
legend("topleft", fill = cols, legend = c("not malnourished = 0", "malnourished = 1"),inset=c(0,-0.15), horiz = T)
```

```{r}
full_mlogr_model <- glm(HW5_ltn2 ~ MOMWEIGHT + momedu0 + momedu1 + numchild2 + numchild3 + wealth1 + wealth2 + wealth3 + wealth4 + MOMAGE + bf1 + bf2 + bf3 + rural + male, data = dem_health_surv, family = binomial)

summary(full_mlogr_model)
```
```{r}
#reorder model to be in order of significance so that table of deviance can show when adding variables isn't adding to model fit
full_mlogr_model <- glm(HW5_ltn2 ~ MOMWEIGHT + numchild2 + numchild3 + MOMAGE + momedu0 + momedu1 + wealth1 + wealth2 + wealth3 + wealth4 + bf1 + bf2 + bf3 + rural + male, data = dem_health_surv, family = binomial)
summary(full_mlogr_model)
```

```{r}
anova(full_mlogr_model, test = "Chisq")
```
```{r}
mlogr_bw_model_v1 <- glm(HW5_ltn2 ~ MOMWEIGHT + numchild2 + numchild3 + MOMAGE + momedu0 + momedu1 + wealth1 + wealth2 + wealth3 + wealth4 + bf1 + bf2 + bf3 + rural, data = dem_health_surv, family = binomial)

summary(mlogr_bw_model_v1)
```
```{r}
anova(mlogr_bw_model_v1, test = "Chisq")
```
```{r}
mlogr_bw_model_v2 <- glm(HW5_ltn2 ~ MOMWEIGHT + numchild2 + numchild3 + MOMAGE + momedu0 + momedu1 + wealth1 + wealth2 + wealth3 + wealth4 + bf1 + bf2 + bf3, data = dem_health_surv, family = binomial)

summary(mlogr_bw_model_v2)
```

```{r}
anova(mlogr_bw_model_v2, test = "Chisq")
```
```{r}
mlogr_bw_model_v3 <- glm(HW5_ltn2 ~ MOMWEIGHT + numchild2 + numchild3 + MOMAGE + momedu0 + momedu1 + wealth1 + wealth2 + wealth3 + wealth4, data = dem_health_surv, family = binomial)

summary(mlogr_bw_model_v3)
```

```{r}
anova(mlogr_bw_model_v3, test = "Chisq")
```


```{r}
hl1 <- hoslem.test(dem_health_surv$HW5_ltn2, fitted(mlogr_bw_model_v3), g= 10)
hl1
cbind(hl1$observed, hl1$expected)
```
```{r}
mlogr_bw_model_v3_probs <- predict(mlogr_bw_model_v3, type = "response")
mlogr_bw_model_v3_pred <- ifelse(mlogr_bw_model_v3_probs > 0.5, "Pred Malnourished","Pred Not Malnourished")
table(mlogr_bw_model_v3_pred, dem_health_surv$HW5_ltn2)

```

```{r}
mlogr_inter_only <- glm(HW5_ltn2 ~ MOMWEIGHT + numchild2 + numchild3 + MOMWEIGHT*numchild2 + MOMWEIGHT*numchild3, data = dem_health_surv, family = binomial)
summary(mlogr_inter_only)

```
```{r}
anova(mlogr_inter_only, test="Chisq")
```
```{r}
hl1 <- hoslem.test(dem_health_surv$HW5_ltn2, fitted(mlogr_inter_only), g= 10)
hl1
cbind(hl1$observed, hl1$expected)
```


```{r}
mlogr_inter_full <- glm(HW5_ltn2 ~ MOMWEIGHT + numchild2 + numchild3 + MOMAGE +  momedu0 + momedu1 + wealth1 + wealth2 + wealth3 + wealth4 + bf1 + bf2 + bf3 + rural + male + MOMWEIGHT*numchild2 + MOMWEIGHT*numchild3, data = dem_health_surv, family = binomial)

summary(mlogr_inter_full)
```
```{r}
anova(mlogr_inter_full, test="Chisq")
```
```{r}
mlogr_inter_v1 <- glm(HW5_ltn2 ~ MOMWEIGHT + numchild2 + numchild3 + MOMAGE +  momedu0 + momedu1 + wealth1 + wealth2 + wealth3 + wealth4 + bf1 + bf2 + bf3 + rural + MOMWEIGHT*numchild2 + MOMWEIGHT*numchild3, data = dem_health_surv, family = binomial)

summary(mlogr_inter_v1)
```
```{r}
mlogr_inter_v2 <- glm(HW5_ltn2 ~ MOMWEIGHT + numchild2 + numchild3 + MOMAGE +  momedu0 + momedu1 + wealth1 + wealth2 + wealth3 + wealth4 + bf1 + bf2 + bf3 +  MOMWEIGHT*numchild2 + MOMWEIGHT*numchild3, data = dem_health_surv, family = binomial)

summary(mlogr_inter_v2)
```
```{r}
mlogr_inter_v3 <- glm(HW5_ltn2 ~ MOMWEIGHT + numchild2 + numchild3 + MOMAGE +  momedu0 + momedu1 + wealth1 + wealth2 + wealth3 + wealth4 +  MOMWEIGHT*numchild2 + MOMWEIGHT*numchild3, data = dem_health_surv, family = binomial)

summary(mlogr_inter_v3)
```
```{r}
mlogr_inter_v4 <- glm(HW5_ltn2 ~ MOMWEIGHT + numchild2 + numchild3 + MOMAGE +  momedu0 + momedu1 +  MOMWEIGHT*numchild2 + MOMWEIGHT*numchild3 + wealth1 + wealth2 + wealth3 + wealth4, data = dem_health_surv, family = binomial)
summary(mlogr_inter_v4)
anova(mlogr_inter_v4, test="Chisq")
```
```{r}
hl1 <- hoslem.test(dem_health_surv$HW5_ltn2, fitted(mlogr_inter_v4), g= 50)
hl1
cbind(hl1$observed, hl1$expected)
```
```{r}
mlogr_inter_v4_probs <- predict(mlogr_inter_v4, type = "response")
mlogr_inter_v4_pred <- ifelse(mlogr_inter_v4_probs > 0.5, "Pred Malnourished","Pred Not Malnourished")
table(mlogr_inter_v4_pred, dem_health_surv$HW5_ltn2)
```


###Testing Hosmer Lemeshow test without momweight and wealthind
```{r}
mlogr_without_mw_and_wealth <- glm(HW5_ltn2 ~ MOMAGE + momedu0 + momedu1 + rural + numchild2 + numchild3 + bf1 + bf2 + bf3, family = binomial, data = dem_health_surv)
summary(mlogr_without_mw_and_wealth)
hl1 <- hoslem.test(dem_health_surv$HW5_ltn2, fitted(mlogr_without_mw_and_wealth), g= 10)
hl1
cbind(hl1$observed, hl1$expected)
anova(mlogr_without_mw_and_wealth, test = "Chisq")

mlogr_without_mw_and_wealth_probs <- predict(mlogr_without_mw_and_wealth, type = "response")
mlogr_without_mw_and_wealth_pred <- ifelse(mlogr_without_mw_and_wealth_probs > 0.5, "Pred Malnourished","Pred Not Malnourished")
table(mlogr_without_mw_and_wealth_pred, dem_health_surv$HW5_ltn2)

```
###marginal effects of numchild
```{r}
plot(predict(glm(HW5_ltn2 ~ MOMWEIGHT + numchild2 + numchild3,data = dem_health_surv, family= binomial), type = "response") ~ MOMWEIGHT, data = dem_health_surv, ylab = "predicted probabilities")
plot(predict(mlogr_bw_model_v3, type = "response") ~ MOMWEIGHT, data = dem_health_surv, ylab = "predicted probabilities")
```
```{r}
#Calculate marginal effects
me_dataset <- dem_health_surv
me_dataset$d_MOMWEIGHT <- mlogr_inter_v4_probs * (1-mlogr_inter_v4_probs) * (-0.105527)
me_dataset$d_MOMAGE <- mlogr_inter_v4_probs * (1-mlogr_inter_v4_probs) * (-0.027911)
me_dataset$d_momedu0 <- mlogr_inter_v4_probs * (1-mlogr_inter_v4_probs) * (0.257753)
me_dataset$d_momedu1 <- mlogr_inter_v4_probs * (1-mlogr_inter_v4_probs) * (0.368120)
me_dataset$d_wealth1 <- mlogr_inter_v4_probs * (1-mlogr_inter_v4_probs) * (0.271465)
me_dataset$d_wealth2 <- mlogr_inter_v4_probs * (1-mlogr_inter_v4_probs) * (-0.065914)
me_dataset$d_wealth3 <- mlogr_inter_v4_probs * (1-mlogr_inter_v4_probs) * (-0.030788)
me_dataset$d_wealth4 <- mlogr_inter_v4_probs * (1-mlogr_inter_v4_probs) * (-0.110240)
mean(me_dataset$d_MOMWEIGHT[me_dataset$LIVCHN==1])
mean(me_dataset$d_MOMWEIGHT[me_dataset$LIVCHN==2])
mean(me_dataset$d_MOMWEIGHT[me_dataset$LIVCHN==3])
```
