---
title: "Computer Workshop 7"
author: "Sean Longman"
date: "14/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(tidyverse)
library(ResourceSelection)
```

## Load data
```{r}
alligato <- read_sav("Regression Modelling Data/alligato.sav")
```

## Clean data for binomial multiple logistic regression
```{r}
alligato <- alligato %>%
  mutate(
    eatsfish = case_when(CHOICE == 1 ~ 1, TRUE ~ 0)
  )

table(select(alligato, c(CHOICE, eatsfish)))
```
### percentage of alligators who prefer fish
```{r}
100*sum(alligato$eatsfish)/nrow(alligato)
```
## plot eatsfish against length using sex as marker

```{r}
colors <- c("#FDAE61","#66BD63")
plot(alligato$LENGTH, alligato$eatsfish, col = colors[factor(alligato$SEX)],
     xlab = "length", ylab = "eatsfish")
```

## Clustered boxplot
```{r}
cols <- rainbow(2, s = 0.5)
boxplot(alligato$LENGTH ~ alligato$eatsfish + alligato$SEX,
        xlab = "sex", ylab = "length", names = c("male","","","female"), col = cols)
legend("topleft", fill = cols, legend = c("eatsfish = 0", "eatsfish = 1"), horiz = T)
```

## Fit simple logistic model
```{r}
fit1 <- glm(eatsfish ~ LENGTH + as.factor(SEX), data = alligato, family = binomial)
summary(fit1)
```
## remove sex from model
```{r}
fit2 <- glm(eatsfish ~ LENGTH, data = alligato, family = binomial)
summary(fit2)
```
## Predict the values
```{r}
alligato$glm_probs <- predict(fit2, type = "response")
```

## Compute marginal effects
```{r}
alligato$d_length <- alligato$glm_probs*(1-alligato$glm_probs)*1.053
```

## Scatter plot of marginal effects against the length variable
```{r}
cols  <- rainbow(2,s=0.5)
plot(alligato$d_length ~ alligato$LENGTH, col = cols)
legend("topright", fill = cols, legend = c("sex = male", "sex = female"), horiz = T)
```

On the logit scale the model is logit(pi) = -2.0794 + 1.0533 * LENGTH
On the odds scale the model is pi/(1-pi) = exp(-2.0794 + 1.0533 * LENGTH) 
                                          = exp(-2.0794)*exp(1.0533^LENGTH)
                                          = exp(-2.7094)*2.867^LENGTH
On the probability scale is pi = 1/(1+exp(-2.0794 + 1.0533 * LENGTH))

### The predicted proability of a 1.6m alligator and a 1.5m alligator eating fish
```{r}
predict(fit2, newdata = data.frame(LENGTH = c(1.6,1.5)), type = "response")
```
## Marginal effect of length on the probability of eating fish for male and female alligators
```{r}
mean(alligato$d_length[alligato$SEX == 1])
mean(alligato$d_length[alligato$SEX == 2])
```
## Hosmer-Lemeshow test
```{r}
hl <- hoslem.test(alligato$eatsfish, fitted(fit2),g = 10)
hl
cbind(hl$observed, hl$expected)
```

## interaction terms

```{r}
fit4 <- glm(eatsfish ~LENGTH + as.factor(SEX), data = alligato, family = binomial)
summary(fit4)
```

```{r}
fit5 <- glm(eatsfish ~LENGTH * as.factor(SEX), data = alligato, family = binomial)
summary(fit5)
```
## Omnibus test
```{r}
anova(fit5, test = "Chisq")
```

Model on the logit scale logit(pi) = -0.920 + 0.559 * LENGTH - 6.699 * SEX(2) + 3.037 * LENGTH*SEX(2)
MALES: logit(pi) = -0.920 + 0.559 * LENGTH
FEMALES: logit(pi) = -0.920 + 0.559 * LENGTH - 6.699 * 1 + 3.037 * LENGTH*1
                    = -7.619 + 3.596 * LENGTH
                    
Model on the odds scale:
pi/(1-pi) = exp(-0.920 + 0.559 * LENGTH - 6.699 * SEX(2) + 3.037 * LENGTH*SEX(2))

MALES: exp(-0.920 + 0.559 * LENGTH) = exp(-0.92)*1.749^LENGTH
FEMALES: exp(7.619) * 36.452^LENGTH

Model on the probability scale:
pi = exp(-0.920 + 0.559 * LENGTH - 6.699 * SEX(2) + 3.037 * LENGTH*SEX(2))/(1+exp(-0.920 + 0.559 * LENGTH - 6.699 * SEX(2) + 3.037 * LENGTH*SEX(2)))

MALES:  exp(-0.92)*1.749^LENGTH/(1+ exp(-0.92)*1.749^LENGTH)
FEMALES: exp(7.619) * 36.452^LENGTH/(1+exp(7.619) * 36.452^LENGTH)

### Predict for 1.6m male and 1.5m female
```{r}
predict(fit5, newdata = data.frame(LENGTH = c(1.6,1.5), SEX = c(1,2)), type = "response")
```
Scatter plot of predicted probabilities
```{r}
alligato$fit5_probs <- predict(fit5, type = "response")
cols  <- rainbow(2,s=0.5)
plot(fit5_probs ~ LENGTH, data = alligato, xlim = c(0,4), ylim = c(0,1), col = cols)
legend("topleft", fill = cols, legend = c("sex = male", "sex = female"), horiz = T)
```

